---
title: "Developing Data Products Wk 2"
author: "Ami S"
date: "11/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview:

This assignment consist of task for creating a web page using R markdown that feature a map created using a Leaflet, and to Host it on Github, Rpubs or Neocities.

## Directions:

The Webpage must contains following details:
* Must contain the date that the document was created 
* must consist of map created by Leaflet.

Loading the Leaflet library before moving forward with the codes.
```{r}
library(leaflet)
```

In this assignment I would like to show few sites around London which are worth visiting.
I would also like to modify my icon in heart shape to show the sites on the maps with 
links to their respective websites attached to it.


```{r}
LondonIcon <- makeIcon(
  iconUrl = "https://www.vectorico.com/download/emoticon/heart-icon.png",
  iconWidth = 38, iconHeight = 85,
  iconAnchorX = 20, iconAnchorY = 94,
  shadowUrl = "http://leafletjs.com/examples/custom-icons/leaf-shadow.png")

LondonSites <- c("<a href = 'https://www.britishmuseum.org/'> British Museum </a>",
                 "<a href = 'https://www.museumoflondon.org.uk/museum-london'> London Meuseum </a>",
                 "<a href = 'https://www.ltmuseum.co.uk/'> LondonTransport Museum </a>",
                 "<a href = 'https://en.wikipedia.org/wiki/London_Bridge'> London Bridge </a>",
                 "<a href = 'https://www.london.gov.uk/about-us/our-building-and-squares/trafalgar-square'> Trafalgar Square </a>",
                 "<a href = 'https://www.londoneye.com/'> London Eye </a>",
                 "<a href = 'https://www.royalparks.org.uk/parks/hyde-park'> Hyde Park </a>",
                 "<a href = 'https://www.visitsealife.com/london/'> Sea Life </a>",
                 "<a href = 'https://www.parliament.uk/bigben/'> Big Ben </a>")

Londonmarkers <- data.frame(
  lat = c(51.5194721, 51.5192157, 51.5131802, 51.5093875, 51.50912047, 51.5042055,51.5084260,51.5015876,51.5055946),
  lng = c(-0.1269577,-0.0962506, -0.1216565,-0.0877534, -0.1285230,-0.1193391,-0.1650868,-0.1244889,-0.1370632))

Londonmarkers %>% leaflet() %>% addTiles() %>% addMarkers(icon = LondonIcon, popup = LondonSites)

```





